Data Builder

### 2019-04-06 notebooks/data_builder.Rmd
update

```{r}
# load the data
psp <- read_rds("../data/per_sig_partial.RDS")

@@

@@

```{r}
# first, turn specials, closures, and builtins to functions
psp <- transform_new_df_w_TS_map(psp, type_map_to_fun)

# any other transformations?
```

```{r}
# make it T0
psp_L0 <- transform_new_df_w_TS_map(psp, type_map_T0_to_r)
```

@@

```{r}
# write it to file for Java processing
write_csv(psp_L0, "../data/partial_L0.csv")
```

```{r}
# read in new one
psp_L0 <- read_csv("../data/partial_L0_subtype.csv.gz")
p
# remove SUBTYPE rows
psp_L0 <- psp_L0[!psp_L0$pkg == "SUBTYPE",]
```

```{r}
# write L1 (which is just psp) to file for Java
write_csv(psp, "../data/partial_L1.csv")

@@

```{r}
# read it back
psp <- read_csv("../data/partial_L1_subtype.csv.gz")

@@

psp_col <- read_csv("../data/partial_L1_collapsed.csv.gz")
psp_L0_col <- read_csv("../data/partial_L0_collapsed.csv.gz")
```

```{r}
# arg counts
# again, Java
L0_arg_sig_c <- read_csv("../data/partial_L0_arg_sig_counts.csv")
L1_arg_sig_c <- read_csv("../data/partial_L1_arg_sig_counts.csv")

@@

# rm []
L0_arg_sig_c[1,"count"] <- 0
L1_arg_sig_c[1,"count"] <- 0

# re sort
L0_arg_sig_c[order(-L0_arg_sig_c$count),] -> L0_arg_sig_c
L1_arg_sig_c[order(-L1_arg_sig_c$count),] -> L1_arg_sig_c

@@

@@

ggsave("../paper/plots/L1_by_fun.pdf",width=10,height=4)
```

@@

```{r}
# L2 Time
psp_L2 <- read_csv("../data/partial_L1_L2.csv.gz")
psp_L2 <- psp_L2[!psp_L2$pkg == "SUBTYPE",]
```

@@

@@

ggsave("../paper/plots/L2_by_fun.pdf",width=10,height=4)
```

@@

```{r}
# ...
list_of_L2_sig_c <- read_csv("../data/partial_L1_arg_sig_counts.csv.gz")

@@

list_of_L2_sig_c$perc_tot <- round(list_of_L2_sig_c$count / sum(list_of_L2_sig_c$count) * 100, 1)

@@

# Arg Poly Count L2
data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=c(list_of_L2_sig_c$count %>% sum - L2_poly_sig$count %>% sum, list_of_L2_sig_c$count %>% sum), Percentage=c(paste0(round(100 * (1 - (L2_poly_sig$count %>% sum / list_of_L2_sig_c$count %>% sum)), 1), "%"), "---")) %>% xtable %>% print(include.rownames=F)
```

@@

poly_count_normalized %>% arrange(-poly_norm) %>% slice(2:6)

>>>>

```{r}
# load the data
psp <- read_rds("../data/promise_big_final.RDS")

psp <- as.tibble(psp)

@@

# first, turn specials, closures, and builtins to functions
psp <- transform_new_df_w_TS_map(psp, type_map_to_fun)

@@

```{r}
# make it T0
psp_L0 <- transform_new_df_w_TS_map(psp, type_map_T0_to_r, unparam = T)
psp_L0 <- lists_to_chars_sig_df(psp_L0)
```

@@

```{r}
# write it to file for Java processing
write_csv(psp_L0, "../data/L0.csv")
```

```{r}
# read in new one
psp_L0 <- read_csv("../data/L0_subtype.csv.gz")

# remove SUBTYPE rows
psp_L0 <- psp_L0[!psp_L0$pkg == "SUBTYPE",]
```

```{r}
# write L1 (which is just psp) to file for Java
write_csv(psp, "../data/L1.csv")

@@

```{r}
# read it back
psp <- read_csv("../data/L1_subtype.csv.gz")

@@

psp_L0_col <- read_csv("../data/L0_collapsed.csv.gz")
psp_col <- read_csv("../data/L1_collapsed.csv.gz")

```{r}
# arg counts
# again, Java
L0_arg_sig_c <- read_csv("../data/L0_arg_sig_counts.csv.gz")
L1_arg_sig_c <- read_csv("../data/L1_arg_sig_counts.csv.gz")

@@

# rm []
# L0_arg_sig_c[1,"count"] <- 0
# L1_arg_sig_c[1,"count"] <- 0
L0_arg_sig_c <- L0_arg_sig_c[2:nrow(L0_arg_sig_c), ]
L1_arg_sig_c <- L1_arg_sig_c[2:nrow(L1_arg_sig_c), ]

# re sort
# L0_arg_sig_c[order(-L0_arg_sig_c$count),] -> L0_arg_sig_c
# L1_arg_sig_c[order(-L1_arg_sig_c$count),] -> L1_arg_sig_c

@@

# if want top 10
plot_L0_df %>% tail

@@

ggsave("../paper/plots/L1_by_fun.pdf",width=10,height=4)

plot_L1_df %>% tail
```

@@

```{r}
# L2 Time
psp_L2 <- read_csv("../data/L1_L2.csv.gz")
psp_L2 <- psp_L2[!psp_L2$pkg == "SUBTYPE",]
```

@@

# gonna remove 2 outliers and talk about them separately
plot_L2_df <- plot_L2_df[1:(nrow(plot_L2_df)-2), ]

# THE L2 PLOT

@@

ggsave("../paper/plots/L2_by_fun.pdf",width=10,height=4)

plot_L2_df %>% tail
```

@@

```{r}
# ...
list_of_L2_sig_c <- read_csv("../data/L1_arg_sig_counts_L2.csv.gz")

@@

# remove last
list_of_L2_sig_c <- list_of_L2_sig_c[1:nrow(list_of_L2_sig_c)-1,]

list_of_L2_sig_c$perc_tot <- round(list_of_L2_sig_c$count / sum(list_of_L2_sig_c$count) * 100, 2)

@@

# Arg Poly Count L2
data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=c(list_of_L2_sig_c$count %>% sum - L2_poly_sig$count %>% sum, list_of_L2_sig_c$count %>% sum), Percentage=c(paste0(round(100 * (1 - (L2_poly_sig$count %>% sum / list_of_L2_sig_c$count %>% sum)), 2), "%"), "---")) %>% xtable %>% print(include.rownames=F)
```

@@

poly_count_normalized %>% arrange(-poly_norm) %>% slice(1:10) %>% xtable %>% print(include.rownames=F)
